---
title: "Trolley Experiment"
author: "Fabio Votta"
date: "The Date"
output: github_document
---

```{r, echo=F}
knitr::opts_chunk$set(message = F, warning = F, fig.align = "center", fig.width = 10, fig.height = 6)
```


## packages

```{r}
pacman::p_load(tidyverse, haven, psych, sjPlot, ggpubr, glue)
```

## data

```{r}
trolley <- read_spss("data/TrolleyExperimentArgumentNew.sav") %>% 
  janitor::clean_names(.) %>% 
  filter(general_finisher == 1) %>% 
  drop_na(t1_eqp_eqp1, t1_eqp_eqp3, t1_eqp_eqp7, t1_eqp_eqp8, t1_eqp_eqp9,
         t1_eqp_eqp11, t1_eqp_eqp12 ,t1_eqp_eqp13, t1_eqp_eqp14, t1_eqp_eqp18,
         t1_eqp_eqp2, t1_eqp_eqp4, t1_eqp_eqp5, t1_eqp_eqp6, t1_eqp_eqp10,
         t1_eqp_eqp15, t1_eqp_eqp16 ,t1_eqp_eqp17, t1_eqp_eqp19, t1_eqp_eqp20,
         t1_szenario1q2, t2_szenario1q2, t1_szenario2q2, t2_szenario2q2) %>% 
  filter(t2_gender != 2) %>% 
  mutate(gender = ifelse(t2_gender == 1, "Men", "Women")) %>% 
  mutate(leftright = t2_pol_alignment) %>% 
  mutate(pol_interest = 5 - t2_pol_interest) %>% 
  mutate(church_attendance = 7 - t2_religion_church) %>% 
  mutate(age = 2018 - as.numeric(t2_year_of_birth)) %>% 
  mutate(university = ifelse(t2_university == 4, 0, 1)) %>% 
  mutate(groups = case_when(
    general_group_control == 1 ~ "Control Group",
    general_group_discussion == 1 ~ "Discussion Group",
    general_group_information == 1 ~ "Information Group",
  )) 
```


## Basic Stats

```{r, analysis}
trolley %>% 
  group_by(university) %>% 
  tally() %>% knitr::kable()

trolley %>% 
  group_by(gender) %>% 
  tally() %>% knitr::kable()

trolley %>% 
  group_by(groups) %>% 
  tally() %>% knitr::kable()

trolley %>% 
  select(leftright, pol_interest, church_attendance, age) %>% 
  describe() %>% knitr::kable()
```

## Factor Analysis

```{r}
eqp <- trolley %>% 
  select(contains("eqp")) %>% 
#  na.omit() %>% 
  select(t1_eqp_eqp1, t1_eqp_eqp3, t1_eqp_eqp7, t1_eqp_eqp8, t1_eqp_eqp9,
         t1_eqp_eqp11, t1_eqp_eqp12 ,t1_eqp_eqp13, t1_eqp_eqp14, t1_eqp_eqp18,
         t1_eqp_eqp2, t1_eqp_eqp4, t1_eqp_eqp5, t1_eqp_eqp6, t1_eqp_eqp10,
         t1_eqp_eqp15, t1_eqp_eqp16 ,t1_eqp_eqp17, t1_eqp_eqp19, t1_eqp_eqp20)

trolley$mean_eqp <- rowMeans(eqp)

trolley <- eqp %>% 
  psych::pca(2, rotate = "varimax") %>% 
  predict.psych(data = eqp) %>% 
  cbind(trolley, .)
  
trolley <- trolley %>% 
  rename(idealism_pca = RC1) %>% 
  rename(relativism_pca = RC2)   
```

## Randomisierung/Descriptives

### Age

```{r}
my_comparisons <- list( c("Control Group", "Discussion Group"), 
                        c("Discussion Group", "Information Group"), 
                        c("Control Group", "Information Group") )

age_compare <- trolley %>% 
  ggplot(aes(groups, age)) +
  geom_violin(aes(fill = groups), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Experimental Groups") + ylab("Age") +
  ggtitle("Age Comparison between Experimental Groups") +
  ggpubr::stat_compare_means(comparisons = my_comparisons) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

age_compare

tidytemplate::ggsave_it(age_compare, width = 10, height = 6)
```
### Gender


```{r}
gender_compare <- sjp.xtab(trolley$groups, trolley$gender, 
         margin = "row", bar.pos = "stack",
         show.summary = TRUE, coord.flip = TRUE, 
         prnt.plot = F)$plot +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_gdocs("Gender") +
  xlab("") +
  ggtitle("Gender Comparison between Experimental Groups") +
  scale_alpha(range = c(0.4, 0.8))

gender_compare

tidytemplate::ggsave_it(gender_compare, width = 10, height = 6)
```


#### Together

```{r, fig.width=14, fig.height=6}
dem_compare <- cowplot::plot_grid(age_compare, gender_compare)

dem_compare

tidytemplate::ggsave_it(dem_compare, width = 14, height = 6)
```


### Idealism

```{r}
my_comparisons <- list( c("Control Group", "Discussion Group"), 
                        c("Discussion Group", "Information Group"), 
                        c("Control Group", "Information Group") )

idealism_pca_compare <- trolley %>% 
  ggplot(aes(groups, idealism_pca)) +
  geom_violin(aes(fill = groups), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Experimental Groups") + ylab("Idealism") +
  ggtitle("Idealism Comparison between Experimental Groups") +
  ggpubr::stat_compare_means(comparisons = my_comparisons) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

idealism_pca_compare

tidytemplate::ggsave_it(idealism_pca_compare, width = 10, height = 6)
```

### Relativism

```{r}
my_comparisons <- list( c("Control Group", "Discussion Group"), 
                        c("Discussion Group", "Information Group"), 
                        c("Control Group", "Information Group") )

relativism_pca_compare <- trolley %>% 
  ggplot(aes(groups, relativism_pca)) +
  geom_violin(aes(fill = groups), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Experimental Groups") + ylab("Relativism") +
  ggtitle("Relativism Comparison between Experimental Groups") +
  ggpubr::stat_compare_means(comparisons = my_comparisons) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

relativism_pca_compare

tidytemplate::ggsave_it(relativism_pca_compare, width = 10, height = 6)
```

#### Together

```{r, fig.width=12, fig.height=6}
uv_compare <- cowplot::plot_grid(relativism_pca_compare, idealism_pca_compare)

uv_compare

tidytemplate::ggsave_it(uv_compare, width = 12, height = 6)
```

### AVs

#### Switch Track

```{r}
my_comparisons <- list( c("Control Group", "Discussion Group"), 
                        c("Discussion Group", "Information Group"), 
                        c("Control Group", "Information Group") )

t1_szenario1q2_compare <- trolley %>% 
  ggplot(aes(groups, t1_szenario1q2)) +
  geom_violin(aes(fill = groups), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Experimental Groups") + ylab("Morally justifiable: Switch Track") +
  ggtitle("'Switch Track' Comparison between Experimental Groups") +
  ggpubr::stat_compare_means(comparisons = my_comparisons) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario1q2_compare

tidytemplate::ggsave_it(t1_szenario1q2_compare, width = 10, height = 6)
```

#### Push Person


```{r}
my_comparisons <- list( c("Control Group", "Discussion Group"), 
                        c("Discussion Group", "Information Group"), 
                        c("Control Group", "Information Group") )

t1_szenario2q2_compare <- trolley %>% 
  ggplot(aes(groups, t1_szenario2q2)) +
  geom_violin(aes(fill = groups), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Experimental Groups") + ylab("Morally justifiable: Push Person") +
  ggtitle("'Push Person' Comparison between Experimental Groups") +
  ggpubr::stat_compare_means(comparisons = my_comparisons) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario2q2_compare

tidytemplate::ggsave_it(t1_szenario2q2_compare, width = 10, height = 6)
```

##### Together

```{r, fig.width=12, fig.height=6}
av_compare <- cowplot::plot_grid(t1_szenario1q2_compare, t1_szenario2q2_compare)

av_compare

tidytemplate::ggsave_it(av_compare, width = 12, height = 6)
```

### Demographics

```{r}

t1_szenario1q2_gender <- trolley %>% 
  ggplot(aes(gender, t1_szenario1q2)) +
  geom_violin(aes(fill = gender), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Gender") + ylab("Morally justifiable: Switch Track") +
  ggtitle("Morally Justifiable to Switch Track by Gender") +
  ggpubr::stat_compare_means(label.x.npc = .4) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario1q2_gender

tidytemplate::ggsave_it(t1_szenario1q2_gender, width = 10, height = 6)

t1_szenario2q2_gender <- trolley %>% 
  ggplot(aes(gender, t1_szenario2q2)) +
  geom_violin(aes(fill = gender), alpha = 0.6) +
  geom_boxplot(width = 0.2) +
  xlab("Gender") + ylab("Morally justifiable: Push Person") +
  ggtitle("Morally Justifiable to Push Person by Gender") +
  ggpubr::stat_compare_means(label.x.npc = .5) +
  ggthemes::scale_fill_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario2q2_gender

tidytemplate::ggsave_it(t1_szenario2q2_gender, width = 10, height = 6)

gender_av_compare1 <- cowplot::plot_grid(t1_szenario1q2_gender, t1_szenario2q2_gender)

gender_av_compare1

tidytemplate::ggsave_it(gender_av_compare1, width = 12, height = 6)
```

#### Scatters

```{r}
t1_szenario1q2_gender <- trolley %>% 
  ggplot(aes(age, t1_szenario1q2)) +
  geom_jitter(aes(color = gender), alpha = 0.6) +
  geom_smooth(aes(color = gender),method = "lm") +
  xlab("Age") + ylab("Morally justifiable: Switch Track") +
  ggtitle("Morally Justifiable to Switch Track by Gender and Age") +
  ggpubr::stat_compare_means(label.x.npc = .4) +
  ggthemes::scale_color_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario1q2_gender

tidytemplate::ggsave_it(t1_szenario1q2_gender, width = 10, height = 6)

t1_szenario2q2_gender <- trolley %>% 
  ggplot(aes(age, t1_szenario2q2)) +
  geom_jitter(aes(color = gender), alpha = 0.6) +
  geom_smooth(aes(color = gender),method = "lm") +
  xlab("Age") + ylab("Morally justifiable: Push Person") +
  ggtitle("Morally Justifiable to Push Person by Gender and Age") +
  ggpubr::stat_compare_means(label.x.npc = .5) +
  ggthemes::scale_color_gdocs("") +
  ggthemes::theme_hc() +
  guides(fill = F)

t1_szenario2q2_gender

tidytemplate::ggsave_it(t1_szenario2q2_gender, width = 10, height = 6)

gender_av_compare2 <- cowplot::plot_grid(t1_szenario1q2_gender, t1_szenario2q2_gender)

gender_av_compare2

tidytemplate::ggsave_it(gender_av_compare2, width = 12, height = 6)
```

## Factor Analysis Table

```{r}
# eqp %>% psych::alpha()
#   psych::pca(2, rotate = "varimax") %>% 
#   .$loadings %>% unclass() %>% as.data.frame() %>% 
#   rownames_to_column("eqp_variable")

strip_away_stuff <- function(x) {
x <- str_remove(x, "t1_eqp_")
x <- parse_number(x) %>% 
  ifelse(. %in% 1:9, paste0("eqp0", .), .) %>% 
  ifelse(. %in% 10:20, paste0("eqp", .), .) 
}

eqp <- eqp %>% 
  set_names(eqp %>% names %>% strip_away_stuff) 

factor_names <- c(`1` = "Idealism",
                  `2` = "Relativism")


factor_analysis <- sjp.pca(eqp, rotation = "varimax", 
        nmbr.fctr = 2, prnt.plot = F, show.cronb = T, 
        show.values = T)$plot  +
  ggthemes::scale_color_gdocs("") +
  ggthemes::theme_hc() +
  ggtitle("Ethical Positions Questionnaire - PCA") +
  facet_grid(~xpos, labeller = as_labeller(factor_names)) +
  labs(captions = "Cronbach's Alpha = 0.80")

factor_analysis

tidytemplate::ggsave_it(factor_analysis, width = 10, height = 6)
```

## Summary Statistics

```{r}
save(trolley, file = "text/data/trolley.Rdata")

trolley %>% 
  select(t1_szenario1q2, t2_szenario1q2, t1_szenario2q2, t2_szenario2q2, idealism_pca, relativism_pca, gender, age, church_attendance, general_group_control, general_group_discussion, general_group_information) %>% 
  describe() %>% 
  select(-vars, -trimmed, -mad, -se) %>% 
  knitr::kable()
```


## Models

```{r}
trolley %<>% 
  mutate(groups = factor(groups)) %>% 
  mutate(gender = factor(gender)) 
```


1.  t1 als AV
2.  t1 als AV und gender interaction (Idealism)
3.  t1 als AV und gender interaction (Relativism)
4.  t2 mit Controls für t1 und für treatments
5.  Modelle aus 4. mit Treatment-Interaktion (Idealism)
6.  Modelle aus 4. mit Treatment-Interaktion (Relativism)

a. Szenario 1 (a = Switch Track)
b. Szenario 2b (b = Push Person)

### Model 1a - Switch Track

```{r, include = F}
fit1_s1 <- lm(t1_szenario1q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance + gender, 
           data = trolley)

r2_1_s1 <- tidytemplate::get_r2_label(fit1_s1, adj = T)

reg1_s1 <- sjPlot::plot_model(fit1_s1, show.p = T, 
                              show.values = T, 
                              value.offset = 0.2, 
                              ci.lvl = .9) +
  ggtitle("Model 1a - Switch Track") +
  scale_x_discrete(labels = c("Relativism", "Idealism", 
                              "Gender (Men/Women)", "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight() +
  labs(caption = glue("Adjusted R Squared: {r2_1_s1}"))


# ggsave(filename = "text/images/reg1_s1.png", width = 8, height = 5)

broom::glance(fit1_s1) %>% knitr::kable()
```

### Model 1b - Push Person

```{r, include = F}
fit1_s2 <- lm(t1_szenario2q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance, 
           data = trolley)

r2_1_s2 <- tidytemplate::get_r2_label(fit1_s2, adj = T)


reg1_s2 <- sjPlot::plot_model(fit1_s2, show.p = T, 
                              show.values = T,
                              value.offset = 0.2, 
                              ci.lvl = .9) +
  ggtitle("Model 1b - Push Person") +
  scale_x_discrete(labels = c("Relativism", "Idealism", 
                              "Gender (Men/Women)", "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight() +
  labs(caption = glue("Adjusted R Squared: {r2_1_s2}"))

reg1_s2

# ggsave(filename = "text/images/reg1_s2.png", width = 8, height = 5)

broom::glance(fit1_s2) %>% knitr::kable()


```

#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg1_s1, reg1_s2, ncol = 1)


ggsave(filename = "text/images/reg1_combined.png", width = 8, height = 9)
```

### Model 2a - Switch Track - Idealism X Gender

```{r, include = F}
fit2_s1_int_idealism <- lm(t1_szenario1q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance + gender +
               gender*idealism_pca, 
           data = trolley)

r2_2_s1 <- tidytemplate::get_r2_label(fit2_s1_int_idealism, adj = T)


sjPlot::plot_model(fit2_s1_int_idealism, show.p = T, show.values = T,
                   value.offset = 0.2, ci.lvl = .9) +
  ggtitle("Model 2a - Switch Track") +
  scale_x_discrete(labels = c("Relativism", 
                              "Idealism X Gender",
                              "Idealism", 
                              "Gender (Men/Women)", "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()  +
  labs(caption = glue("Adjusted R Squared: {r2_2_s1}")) -> reg2_s1_int_idealism

reg2_s1_int_idealism

# ggsave(filename = "text/images/reg2_s1_int_idealism.png", width = 8, height = 5)

broom::glance(fit2_s1_int_idealism) %>% knitr::kable()

get_model_data(fit2_s1_int_idealism, type = "pred",
               terms = c("idealism_pca", "gender")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 2a - Switch Track - Idealism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  ylab("Morally justifiable: Switch Track") +
  xlab("Idealism") 


# ggsave(filename = "text/images/reg2_s1_int2_idealism.png", width = 8, height = 5)
```




### Model 2b - Push Person - Idealism X Gender

```{r, include = F}
fit2_s2_int_idealism <- lm(t1_szenario2q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance + gender +
               gender*idealism_pca, 
           data = trolley)

r2_2_s2 <- tidytemplate::get_r2_label(fit2_s2_int_idealism, adj = T)

sjPlot::plot_model(fit2_s2_int_idealism, show.p = T, show.values = T,
                   value.offset = 0.2, ci.lvl = .9) +
  ggtitle("Model 2b - Push Person") +
  scale_x_discrete(labels = c("Relativism", 
                              "Idealism X Gender",
                              "Idealism", 
                              "Gender (Men/Women)", "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight() +
  labs(caption = glue("Adjusted R Squared: {r2_2_s2}")) -> reg2_s2_int_idealism

reg2_s2_int_idealism

# ggsave(filename = "text/images/reg2_s2_int_idealism.png", width = 8, height = 5)

broom::glance(fit2_s2_int_idealism) %>% knitr::kable()

get_model_data(fit2_s2_int_idealism, type = "pred",
               terms = c("idealism_pca", "gender")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 2b - Push Person - Idealism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  ylab("Morally justifiable: Push Person") +
  xlab("Idealism") 


# ggsave(filename = "text/images/reg2_s2_int2_idealism.png", width = 8, height = 5)
```

#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg2_s1_int_idealism, reg2_s2_int_idealism, ncol = 1)


ggsave(filename = "text/images/reg2_c1_idealism.png", width = 8, height = 9)
```

#### Both Interactions

```{r}
bind_rows(
  get_model_data(fit2_s1_int_idealism, type = "pred",
               terms = c("idealism_pca", "gender"), ci.lvl = .9) %>% 
            mutate(type = "Model 2a - Switch Track"),  
  get_model_data(fit2_s2_int_idealism, type = "pred",
               terms = c("idealism_pca", "gender"), ci.lvl = .9) %>% 
            mutate(type = "Model 2b - Push Person")
  ) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 2 - Idealism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  facet_wrap(~type) +
  ylab("Morally justifiable 1 - 11") +
  xlab("Idealism")  
  
ggsave(filename = "text/images/reg2_c2_idealism.png", width = 8, height = 5)

```


### Model 3a - Switch Track - Relativism X Gender

```{r, include = F}
fit3_s1_int_relativism <- lm(t1_szenario1q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance + gender +
               gender*relativism_pca, 
           data = trolley)

r2_3_s1 <- tidytemplate::get_r2_label(fit3_s1_int_relativism, adj = T)


sjPlot::plot_model(fit3_s1_int_relativism, show.p = T, show.values = T,
                   value.offset = 0.2, ci.lvl = .9) +
  scale_x_discrete(labels = c("Relativism X Gender", 
                              "Relativism",
                              "Idealism", 
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 3a - Switch Track") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()  +
  labs(caption = glue("Adjusted R Squared: {r2_3_s1}")) -> reg3_s1_int_relativism

reg3_s1_int_relativism

# ggsave(filename = "text/images/reg3_s1_int_relativism.png", width = 8, height = 5)

broom::glance(fit3_s1_int_relativism) %>% knitr::kable()

get_model_data(fit3_s1_int_relativism, type = "pred",
               terms = c("relativism_pca", "gender")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 3a - Switch Track - Relativism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  ylab("Morally justifiable: Switch Track") +
  xlab("Relativism") 


# ggsave(filename = "text/images/reg3_s1_int2_relativism.png", width = 8, height = 5)
```

### Model 3b - Push Person- Relativism X Gender

```{r, include = F}
fit3_s2_int_relativism <- lm(t1_szenario2q2 ~ idealism_pca + relativism_pca + 
             gender + age + church_attendance + gender +
               gender*relativism_pca, 
           data = trolley)


r2_3_s2 <- tidytemplate::get_r2_label(fit3_s2_int_relativism, adj = T)

sjPlot::plot_model(fit3_s2_int_relativism, show.p = T, show.values = T,
                   value.offset = 0.2, ci.lvl = .9) +
  scale_x_discrete(labels = c("Relativism X Gender", 
                              "Relativism",
                              "Idealism", 
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 3b - Push Person") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()  +
  labs(caption = glue("Adjusted R Squared: {r2_3_s2}")) -> reg3_s2_int_relativism

reg3_s2_int_relativism

# ggsave(filename = "text/images/reg3_s2_int_relativism.png", width = 8, height = 5)

broom::glance(fit3_s2_int_relativism) %>% knitr::kable()

get_model_data(fit3_s2_int_relativism, type = "pred",
               terms = c("relativism_pca", "gender")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 3b - Push Person - Relativism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  ylab("Morally justifiable: Push Person") +
  xlab("Relativism") 


# ggsave(filename = "text/images/reg3_s2_int2_relativism.png", width = 8, height = 5)
```

#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg3_s1_int_relativism, reg3_s2_int_relativism, ncol = 1)


ggsave(filename = "text/images/reg3_c1_relativism.png", width = 8, height = 9)
```

#### Both Interactions

```{r}
bind_rows(
  get_model_data(fit3_s1_int_relativism, type = "pred",
               terms = c("relativism_pca", "gender"), ci.lvl = .9) %>% 
            mutate(type = "Model 3a - Switch Track"),  
  get_model_data(fit3_s2_int_relativism, type = "pred",
               terms = c("relativism_pca", "gender"), ci.lvl = .9) %>% 
            mutate(type = "Model 3b - Push Person")
  ) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 3 - Relativism X Gender") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Gender") +
  ggthemes::scale_color_fivethirtyeight("Gender") +
  facet_wrap(~type) +
  ylab("Morally justifiable 1 - 11") +
  xlab("Relativism")  
  
ggsave(filename = "text/images/reg3_c2_relativism.png", width = 8, height = 5)

```

### Model 4a - Switch Track

```{r, include = F}
fit4_s1 <- lm(t2_szenario1q2 ~ t1_szenario1q2 + idealism_pca + relativism_pca +
             gender + age + church_attendance +
             groups, 
           data = trolley)

r2_4_s1 <- tidytemplate::get_r2_label(fit4_s1, adj = T)


sjPlot::plot_model(fit4_s1, show.p = T, show.values = T, value.offset = 0.4, ci.lvl = .9) +
  ggtitle("Model 4a - Opinion Change - Switch Track") +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()  +
  labs(caption = glue("Adjusted R Squared: {r2_4_s1}"))  -> reg4_s1

reg4_s1

# ggsave(filename = "text/images/reg4_s1.png", width = 8, height = 5)

broom::glance(fit4_s1) %>% knitr::kable()
```


### Model 4b - Push Person

```{r, include = F}
fit4_s2 <- lm(t2_szenario2q2 ~ t1_szenario2q2 + idealism_pca + relativism_pca + 
             gender + age + church_attendance +
             groups, 
           data = trolley)

r2_4_s2 <- tidytemplate::get_r2_label(fit4_s2, adj = T)


sjPlot::plot_model(fit4_s2, show.p = T, show.values = T, value.offset = 0.4, ci.lvl = .9) +
  ggtitle("Model 4b - Opinion Change - Push Person") +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()  +
  labs(caption = glue("Adjusted R Squared: {r2_4_s2}"))  -> reg4_s2

reg4_s2

# ggsave(filename = "text/images/reg4_s2.png", width = 8, height = 5)

broom::glance(fit4_s2) %>% knitr::kable()
```

#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg4_s1, reg4_s2, ncol = 1)


ggsave(filename = "text/images/reg4_combined.png", width = 8, height = 9)
```

### Model 5a - Switch Track - Idealism

```{r, include = F}
fit5_s1 <- lm(t2_szenario1q2 ~ t1_szenario1q2 + idealism_pca + relativism_pca + 
             gender + age + church_attendance +
             groups * idealism_pca, 
           data = trolley)

r2_5_s1 <- tidytemplate::get_r2_label(fit5_s1, adj = T)


sjPlot::plot_model(fit5_s1, show.p = T, 
                              show.values = T, value.offset = 0.4, ci.lvl = .9) +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism",
                              "Idealism X Information Group",
                              "Idealism X Discussion Group",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 5a - Opinion Change - Switch Track") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()   +
  labs(caption = glue("Adjusted R Squared: {r2_5_s1}")) -> reg5_s1

reg5_s1

# ggsave(filename = "text/images/reg5_s1.png", width = 8, height = 5)

broom::glance(fit5_s1) %>% knitr::kable()

get_model_data(fit5_s1, type = "pred",
               terms = c("idealism_pca", "groups")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 5a - Switch Track - Idealism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  ylab("Morally justifiable: Switch Track") +
  xlab("Idealism") 

# ggsave(filename = "text/images/reg5_s1_int.png", width = 8, height = 5)
```

### Model 5b - Push Person - Idealism

```{r, include = F}
fit5_s2 <- lm(t2_szenario2q2 ~ t1_szenario2q2 + idealism_pca + relativism_pca + 
             gender + age + church_attendance +
             groups * idealism_pca, 
           data = trolley)

r2_5_s2 <- tidytemplate::get_r2_label(fit5_s2, adj = T)


sjPlot::plot_model(fit5_s2, show.p = T, 
                              show.values = T, value.offset = 0.4, ci.lvl = .9) +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism",
                              "Idealism X Information Group",
                              "Idealism X Discussion Group",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 5b - Opinion Change - Push Person") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight()   +
  labs(caption = glue("Adjusted R Squared: {r2_5_s2}")) -> reg5_s2

reg5_s2

# ggsave(filename = "text/images/reg5_s2.png", width = 8, height = 5)

broom::glance(fit5_s2) %>% knitr::kable()

get_model_data(fit5_s2, type = "pred",
               terms = c("idealism_pca", "groups")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 5b - Push Person - Idealism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  ylab("Morally justifiable: Push Person") +
  xlab("Idealism") 

# ggsave(filename = "text/images/reg5_s2_int.png", width = 8, height = 5)
```


#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg5_s1, reg5_s2, ncol = 1)


ggsave(filename = "text/images/reg5_c1_idealism.png", width = 8, height = 9)
```

#### Both Interactions

```{r}
bind_rows(
  get_model_data(fit5_s1, type = "pred",
               terms = c("idealism_pca", "groups"), ci.lvl = .9) %>% 
            mutate(type = "Model 5a - Switch Track"),  
  get_model_data(fit5_s2, type = "pred",
               terms = c("idealism_pca", "groups"), ci.lvl = .9) %>% 
            mutate(type = "Model 5b - Push Person")
  ) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 5 - Idealism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  facet_wrap(~type) +
  ylab("Morally justifiable 1 - 11") +
  xlab("Idealism")  
  
ggsave(filename = "text/images/reg5_c2_idealism.png", width = 8, height = 5)

```

### Model 6a - Switch Track - Relativism

```{r, include = F}
fit6_s1 <- lm(t2_szenario1q2 ~ t1_szenario1q2 + idealism_pca + relativism_pca + 
             gender + age + church_attendance +
             groups * relativism_pca, 
           data = trolley)

r2_6_s1 <- tidytemplate::get_r2_label(fit6_s1, adj = T)


sjPlot::plot_model(fit6_s1, show.p = T, 
                              show.values = T, value.offset = 0.4, ci.lvl = .9) +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism X Information Group",
                              "Relativism X Discussion Group",
                              "Relativism",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 6a - Opinion Change - Switch Track") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight() +
  labs(caption = glue("Adjusted R Squared: {r2_6_s1}"))  -> reg6_s1

reg6_s1

# ggsave(filename = "text/images/reg6_s1.png", width = 8, height = 5)

broom::glance(fit6_s1) %>% knitr::kable()

get_model_data(fit6_s1, type = "pred",
               terms = c("relativism_pca", "groups")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 6a - Switch Track - Relativism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  ylab("Morally justifiable: Switch Track") +
  xlab("Relativism") 

# ggsave(filename = "text/images/reg6_s1_int.png", width = 8, height = 5)
```


### Model 6b - Push Person - Relativism


```{r, include = F}
fit6_s2 <- lm(t2_szenario2q2 ~ t1_szenario2q2 + idealism_pca + relativism_pca + 
             gender + age + church_attendance +
             groups * relativism_pca, 
           data = trolley)

r2_6_s2 <- tidytemplate::get_r2_label(fit6_s2, adj = T)


sjPlot::plot_model(fit6_s2, show.p = T, 
                              show.values = T, value.offset = 0.4, ci.lvl = .9) +
  scale_x_discrete(labels = c("Mor. Justifiable T1", 
                              "Relativism X Information Group",
                              "Relativism X Discussion Group",
                              "Relativism",
                              "Idealism", 
                              "Information Group",
                              "Discussion Group",
                              "Gender (Men/Women)", 
                              "Church Attendance",
                              "Age")) +
  ggtitle("Model 6b - Opinion Change - Push Person") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight() +
  labs(caption = glue("Adjusted R Squared: {r2_6_s2}"))  -> reg6_s2

reg6_s2

# ggsave(filename = "text/images/reg6_s2.png", width = 8, height = 5)

broom::glance(fit6_s2) %>% knitr::kable()

get_model_data(fit6_s2, type = "pred",
               terms = c("relativism_pca", "groups")) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 6b - Push Person - Relativism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  ylab("Morally justifiable: Push Person") +
  xlab("Relativism") 

# ggsave(filename = "text/images/reg6_s2_int.png", width = 8, height = 5)
```



#### Both Models

```{r, fig.width = 7, fig.height = 8}
cowplot::plot_grid(reg6_s1, reg6_s2, ncol = 1)


ggsave(filename = "text/images/reg6_c1_relativism.png", width = 7, height = 8)
```

#### Both Interactions

```{r}

bind_rows(
  get_model_data(fit6_s1, type = "pred",
               terms = c("relativism_pca", "groups"), ci.lvl = .9) %>% 
            mutate(type = "Model 6a - Switch Track"),  
  get_model_data(fit6_s2, type = "pred",
               terms = c("relativism_pca", "groups"), ci.lvl = .9) %>% 
            mutate(type = "Model 6b - Push Person")
  ) %>% 
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, 
                  ymax = conf.high, 
                  fill = group), alpha = 0.11) +
  geom_line(aes(color = group), size = 1.2) +
  ggtitle("Model 6 - Relativism X Experimental Groups") +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_fivethirtyeight("Experimental Groups") +
  ggthemes::scale_color_fivethirtyeight("Experimental Groups") +
  facet_wrap(~type) +
  ylab("Morally justifiable 1 - 11") +
  xlab("Relativism")  

ggsave(filename = "text/images/reg6_c2_relativism.png", width = 8, height = 5)

```